---
title: "Guys"
author: "Bada!"
date: "11, Novermber,2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastf <-filter(avast,sex=="gal")
avastm <-filter(avast,sex=="guy")
avastq <-filter(avast,LGBTQ=="gay")
avastd <-filter(avast,DrugUser=="yes")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!These research will consider five different Sub group, First Every body in the data group, DrugUsers, Gays, Guys, gays. Each will be analise by Graphical Descriptive Result, Numerical Descriptive Results, and the Inferential Results. with these methods we will able to determine the effectiveness of the new drug (Abacavirinol) on each sub-group.

$H_0$ There is no relationship between the use of new drug (abacavirno) and Guy (Male) contacting Aids.

$H_1$  There is relationship between the use of new drug (abacavirnol) and Guy (Male) that are contacting Aids, The drug is not effective on Guy (Male) that took it.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
The following methods will be used in the reaseach. Graphical Descriptive Result, Bar chart will be use to show effectiveness of the treatment in percentage of the population, Numerical Descriptive Results,will show the actualll number of people that were treated or the number of peoploe that took the New drug (abacavirinol) and people that took Placebo   and the Inferential Results. analysis the p-Value of the with these methods, the  confidence interval and the he estimated odds ratio. 

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results
Bar chart will be use for the descriptive reseach it will show resuit in percentage of the Guy (Male) population, this will show the effectiveness of the new drug. 

### Graphical Descriptive Results
```{r}
barchartGC(~infected + treatment,data=avastm,type="percent")
```
The graphical resuit show that the new Aid drug (abacavirnol)is not effectiveness on Guy (Male) population. Guy (Male) that took the drug about 59 percent of Guy (Male) that used the drug are infected by Aids comparid to 41 percent of Guy (Male) that used the Placebo. 

$H_0$ There is no relationship between the use of new drug (abacavirno) and Guy (Male) contacting Aids.

$H_1$  There is relationship between the use of new drug (abacavirnol) and Guy (Male) contacting Aids, The drug is not effective on Guy (Male) population that took it.

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

### Numerical Descriptive Results


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs (~infected + treatment,data=avastm)
rowPerc(table1)
colPerc(table1)
```
Numerical Descriptive Results show that the new Aid drug (abacavirnol) is not effectiveness on Guy (Male) population. Among Guy (Male) that took the drug 58.82 were infected by Aid and 41.18 of Guy (Male) that used placebo have Aids. this show that the drug is not effective on Guy (Male) that use it.

## Inferential Results
  

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
``` 
Inferential Results show that the drug (abacavirnol) is not effectiveness on Guy (Male), Observed counts treatment show that 210 of guy (Males) that took the new drug (Abacavirnol) were infected by Aid and 147 of Guy (Male) that used placebo are  infected by Aids. this show that the drug is not effective on Guy (Male).  the experiment also show that the P-Vallue= 6.596.which is higher that our convectionaL treashold Of 0.5, also the  confidence interval: 1.240408 1.925729, compaired to ratio 1:1  when they did not take the drug. So the new Drug (abacavirnol) is not effective on Guy (males) per the experiment.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
The graphical resuit show ineffectiveness of new Aid drug (abacavirnol) on Guy (Male) population. that Guy (Male) that took the drug 59 percent of Guy (Male) that used the drug are been infected by Aids comparid to 41 percent of Guy (Male) that used the Placebo.
   
   Aslo Numerical Descriptive Results show ineffectiveness of new Aid drug (abacavirnol) on Guy (Male) population.  Guy (Male) that took the drug 58.82 were infected by Aid and 41.18 of Guy (Male) that used placebo were infected by Aids. this show that the drug is not effective on Guy (Male) that use it.
   
   Inferential Results show the ineffectiveness of the drug, Observed counts treatment show that 210 of guy (Males) that took the new drug (Abacavirnol) were infected by Aid and 147 of Guy (Male) that used placebo have Aids. this show that the drug is not effective on Guy (Male).   Also the P-Vallue= 6.596. the  confidence interval:1.240408 1.925729, the estimated odds ratio = 1.543902 compaired to ratio 1 to 1 when they did not take the drug. The New drug (abacavirnol) did not have relationship with Aids, it did not reduce the chances of been infected by Aids . So the new Drug (abacavirnol) is not effective per the experiment.
    
